---
title: "Cultural Data Science exam script"
author: "Frida Hæstrup and Marie Mortensen"
date: "11/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Packages and functions
```{r library}
source("../functions/functions_packages.R")
```


# Bills
### Scraping
### Data transformation
### Lemmatization
### Keyword search 


# Citizen Proposals

### Scraping
Firstly, the function scraping from websites with infinite scroll is applied
```{r scrape}
citizen <- infinite_scrape(url = "https://www.borgerforslag.dk/api/proposals/search", n_pages = 200)
```

### Data transformation
Afterwards, date format is changed
```{r transformation}
#the dates are currently in danish and are not following any general formats which will be changed now.
date_list <- stringr::str_match(citizen$date, "([0-9]{2}). ([a-z]*) ([0-9]{4})")[,2:4] #this uses the stringr package to make three word groups from the column containing the date. We need these groups in order to change the month name to numeric  

#below is a  data frame that will be used to match the month name in the original date column with a numeric replacement
month_match <- data.frame( 
  month_no = c(seq(01, 12, 01)),
  month_name = c("januar",
                 "februar",
                 "marts",
                 "april",
                 "maj",
                 "juni",
                 "juli",
                 "august",
                 "september",
                 "oktober",
                 "november",
                 "december"),
  month_name_us = c("january", #adding translated month names in case it will be necessary to have a column with them
                    "february",
                    "march",
                    "april",
                    "may",
                    "june",
                    "july",
                    "august",
                    "september",
                    "october",
                    "november",
                    "december")
  ) %>% mutate(month_name = as.character(month_name),
               month_name_us =  as.character(month_name_us))

#this takes the list to transform and changes the names from month names to month number by matching them in the data frame that has the names and corresponding number
date_list[,2] <- plyr::mapvalues(date_list[,2],
                                 from =month_match$month_name,
                                 to = month_match$month_no)

#next, they are combined together using paste() that separates them with a -
date_list_new <- paste(date_list[,3], date_list[,2], date_list[,1], sep = "-")

citizen <- citizen %>% #lastly they are added to the data frame containing the other information
  mutate(date = as.Date.character(as.character(date_list_new)), #changing to date format
  month = plyr::mapvalues(date_list[,2],
                          from = month_match$month_no,
                          to = month_match$month_name_us)) %>%
  mutate(year = date_list[,3]) %>%
  #mutate(year = str_extract_all(date, "[0-9]{4}")) %>%
  unite("month_year", month:year, sep = " ", remove = F)
```

### Separating each government
```{r}
#rasmussen <- citizen %>% subset(government=="Rasmussen")

#frederiksen <- citizen %>% subset(government=="Frederiksen")
```

### Lemmatizing words
Below the original titles are transformed to their lemmas 
```{r lemmatization}
lemma_words <- read.csv("../data/borgerforslag_lemmatized.csv")
lemma_words$date <- as.Date.character(lemma_words$date)
lemma_words$pm <- ifelse(lemma_words$date > "2019-06-05", "Frederiksen", "Rasmussen") 
lemma_gov <- read.csv("../mari.csv")
```

### Extracting proportion of titles containing keywords
```{r keyword}
keyword_list <- c("skat", "kontanthjælp", "udlænding", "invandr", "politi", "sundhed", "erhverv")

ras_citizen <- keyword_search(lemma_words$title_dup[lemma_words$pm == "Rasmussen"], keyword_list)
fred_citizen <- keyword_search(lemma_words$title_dup[lemma_words$pm == "Frederiksen"], keyword_list)
  
ras_bills <- keyword_search(lemma_gov$title[lemma_gov$pm == "Rasmussen"], keyword_list)
fred_bills <- keyword_search(lemma_gov$title[lemma_gov$pm == "Frederiksen"], keyword_list)

```

### Making pie charts with highcharts
```{r pie}
pie_plot <- function(keyword_df, bill_type, government, palette = "Dark2"){
  plot <- keyword_df %>%
  ggplot(aes(x="", y=percent, fill=keyword)) + 
  geom_bar(stat="identity", width=1) + 
  coord_polar("y", start=0) + # Convert to pie (polar coordinates) and add labels
  geom_text(aes(label = paste0(round(percent, digits = 2), "%")), 
            position = position_stack(vjust = 0.7),#vjust = 0.8
            family = "Times New Roman")  + 
  scale_fill_brewer(palette = palette) + # Add color scale (hex colors)
  labs(x = NULL, y = NULL, fill = NULL, title = paste("Keyword percentages", bill_type, "-", government, sep = " "))+ # Remove labels and add title
  theme_classic() + # Tidy up the theme
  theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, size = 12, family = "Times New Roman"))
  return(plot)
}


ras_citi_plot <- pie_plot(ras_citizen, "citizen proposals", "Rasmussen", palette = "Paired")

legend <- get_legend(ras_citi_plot)
ras_citi_plot + theme(legend.position="none")

fred_citi_plot <- pie_plot(fred_citizen, "citizen proposals", "Frederiksen", palette = "Paired")
fred_citi_plot <- fred_citi_plot + theme(legend.position="none")

ras_bills_plot <- pie_plot(ras_bills, "bills", "Rasmussen", palette = "Paired")
ras_bills_plot <- ras_bills_plot + theme(legend.position="none")

fred_bills_plot <- pie_plot(fred_bills,"bills", "Rasmussen", palette = "Paired")
fred_bills_plot <- fred_bills_plot + theme(legend.position="none")

pacman::p_load(gridExtra, cowplot) 

gridExtra::grid.arrange(ras_citi_plot, ras_bills_plot, fred_citi_plot, fred_bills_plot, legend)

```

plot experiment
```{r}
# 1. Create the plots
#++++++++++++++++++++++++++++++++++
# Create a box plot with a top legend position
bp <- ggplot(ras_bills, aes(x="", y=percent, fill=keyword)) +
  geom_bar(stat="identity", width=1) + 
  coord_polar("y", start=0) + # Convert to pie (polar coordinates) and add labels
  theme(legend.position = "top")

# Create a violin plot
vp <- ggplot(fred_bills, aes(x="",y=percent, fill=keyword)) +
  geom_bar(stat="identity", width=1) + 
  coord_polar("y", start=0) + # Convert to pie (polar coordinates) and add labels
  theme(legend.position="none")

# 2. Save the legend
#+++++++++++++++++++++++
legend <- get_legend(bp)
# 3. Remove the legend from the box plot
#+++++++++++++++++++++++
bp <- bp + theme(legend.position="none")
# 4. Create a blank plot
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()


gridExtra::grid.arrange(bp, vp, legend)


```




